---
title: "detrendr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>")
```

Detrend image series.

[![Travis-CI Build Status](https://travis-ci.org/rorynolan/detrendr.svg?branch=master)](https://travis-ci.org/rorynolan/detrendr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rorynolan/detrendr?branch=master&svg=true)](https://ci.appveyor.com/project/rorynolan/detrendr)
[![Coverage Status](https://img.shields.io/codecov/c/github/rorynolan/detrendr/master.svg)](https://codecov.io/github/rorynolan/detrendr?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/detrendr)](https://cran.r-project.org/package=detrendr)
![RStudio CRAN downloads](http://cranlogs.r-pkg.org/badges/grand-total/detrendr)
![RStudio CRAN monthly downloads](http://cranlogs.r-pkg.org/badges/detrendr)
[![Rdocumentation](http://www.rdocumentation.org/badges/version/detrendr)](http://www.rdocumentation.org/packages/detrendr)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

# Installation
To install the release version (recommended) from CRAN, in R, enter
```{r Install detrendr, eval=FALSE}
install.packages("detrendr")
```
To install the development version, in R, first install `devtools` via `install.packages("devtools")`. Then enter
```{r Install detrendr dev, eval=FALSE}
devtools::install_github("rorynolan/detrendr")
```

# Use 

First let's load the library: 
```{r load}
library(detrendr)
```

## An image in need of detrending
The package contains a sample image series which can be found at  
`system.file("extdata", "bleached.tif", package = "detrendr")`. It's 500 frames of diffusing fluorescent particles which are bleaching over the course of the acquisition. We can see they're bleaching by displaying every 99th frame.

```{r visualize bleaching, fig.height=3.3, fig.width=11}
library(magrittr)
path <- system.file("extdata", "bleached.tif", package = "detrendr")
img <- ijtiff::read_tif(path, msg = FALSE)
every100th <- purrr::map(seq(1, dim(img)[4], by = 99), ~ img[, , 1, .]) %>% 
  purrr::reduce(~ cbind(.x, max(img), .y))
ijtiff::display(every100th)
```

## Detrending
We see that the intensity is much lower for the last frame, this is because the image series has been bleached. We can correct for this. 

```{r detrend, fig.height=3.3, fig.width=11}
system.time(corrected_exp <- img_detrend_exp(img, "auto", purpose = "FFS",
                                             seed = 0, parallel = 2))["elapsed"]
every100th <- purrr::map(seq(1, dim(img)[4], by = 99), 
                         ~ corrected_exp[, , 1, .]) %>% 
  purrr::reduce(~ cbind(.x, max(img), .y))
ijtiff::display(every100th)
```

So we see that the corrected series does not have this drop-off in intensity. 

# Vignette
For more detailed instruction on how to use the package, see the package [vignette](https://cran.r-project.org/web/packages/detrendr/vignettes/detrendr.html).

# Contribution
Contributions to this package are welcome. The preferred method of contribution is through a github pull request. Feel free to contact me by creating an issue. Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
