---
title: "detrendr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>")
```

Detrend image series.

[![Travis-CI Build Status](https://travis-ci.org/rorynolan/detrendr.svg?branch=master)](https://travis-ci.org/rorynolan/detrendr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rorynolan/detrendr?branch=master&svg=true)](https://ci.appveyor.com/project/rorynolan/detrendr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/detrendr)](https://cran.r-project.org/package=detrendr)
![RStudio CRAN downloads](http://cranlogs.r-pkg.org/badges/grand-total/detrendr)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

# Installation
To install the release version (recommended) from CRAN, in R, enter
```{r Install detrendr, eval=FALSE}
install.packages("detrendr")
```
To install the development version, in R, first install `devtools` via `install.packages("devtools")`. Then enter
```{r Install detrendr dev, eval=FALSE}
devtools::install_github("rorynolan/detrendr")
```

# Use 

First let's load the library: 
```{r load}
library(detrendr)
```

## Image I/O and display
The package contains a sample image series which can be found at `system.file("extdata", "cells.tif", package = "detrendr")`. Let's read it in and inspect the first and last frames:
```{r display}
path <- system.file("extdata", "bleached.tif", package = "detrendr")
img <- ijtiff::read_tif(path)[, , 1, ]  # first channel
dim(img)  # img has 500 frames
mean(img[, , 1])  # first frame
mean(img[, , 500])  # last frame
```

## Detrending
We see that the intensity is much lower for the last frame, this is because the image series has been bleached. We can correct for this (and check how long it takes):
```{r detrend}
system.time(corrected <- img_detrend_exp(img, "auto", 
                                         seed = 0, parallel = 2))["elapsed"]
mean(corrected[, , 1])  # first frame
mean(corrected[, , 500])  # last frame
```

So we see that the corrected series does not have this drop-off in intensity. 

# Vignette
For more detailed instruction on how to use the package, see `vignette("detrendr")`.

# Contribution
Contributions to this package are welcome. The preferred method of contribution is through a github pull request. Feel free to contact me by creating an issue. Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
